On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement

### 2024-07-17 manuscript/sections/conclusion.tex
license: add reuse compatibility
project: initial run pre-commit against all files

In this work, we systematically examined the means, costs, and the system-level impacts of the 24/7 carbon-free energy matching. 
We find that 24/7 matching is a viable and effective strategy for electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
Voluntary commitments to the hourly matching strategy have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
The evidence holds across geographical locations and is robust to sensitivity analyses.
Even as grids become cleaner over time, the 24/7 matching strategy retains its significance in reducing system-level emissions, which is essential in light of evolving national energy and climate policies.

>>>>

% SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
%
% SPDX-License-Identifier: CC-BY-4.0

In this work, we systematically examined the means, costs, and the system-level impacts of the 24/7 carbon-free energy matching.
We find that 24/7 matching is a viable and effective strategy for clean electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
The evidence holds across different geographical locations.
Even as grids become cleaner over time, the 24/7 matching strategy retains its significance in reducing system-level emissions, which is essential in light of evolving national energy and climate policies.
Voluntary commitments to the hourly matching strategy have a further transformative effect on electricity systems by creating an early market for advanced energy technologies, such as long-duration energy storage and clean firm power generators.

### 2024-07-17 manuscript/sections/discussion.tex

% Limitations: a point on DSM
Fourth, participating consumers have an inflexible demand, i.e., no demand-side management is considered.
In reality, many \gls{ci} consumers have some degree of demand flexibility, which they can use to adjust their consumption as needed based on grid signals, such as the wholesale market price and the average emission rate of the local electricity mix.
Moreover, some consumers, such as data centers and cloud computing providers, can shift their load also in space, i.e., to shift computing
jobs and associated power loads across data center locations \cite{koningsteinWeNowMore2021}.
In the recent work, Riepin~\&~Brown (2023) explore how space-time load-shifting flexibility can be used to meet high 24/7 CFE targets, as well as what potential benefits it may offer to participating energy buyers and to the rest of the energy system \cite{riepin-zenodo-spacetime247CFE}.

>>>>

% Limitations: a point on DSM
Fourth, participating consumers have an inflexible demand, i.e., no demand-side management is considered.
In reality, many \gls{ci} consumers have some degree of demand flexibility, which they can use to adjust their consumption as needed based on grid signals, such as the wholesale market price and the average emission rate of the local electricity mix.
Moreover, some consumers, such as data centers and cloud computing providers, can shift their load also in space, i.e., to shift computing jobs and associated power loads across data center locations \cite{koningsteinWeNowMore2021}.
The ability to shift power loads in time and space can play a significant role in achieving hourly carbon-free energy matching by 2030, as more applications and engineering solutions become available \cite{radovanovicCarbonAwareComputingDatacenters2021,radovanovicIEEE2023,koningsteinWeNowMore2021}.
In the recent work, Riepin~\&~Brown (2023) explore how space-time load-shifting flexibility can be used to meet high 24/7 CFE targets. \cite{riepin-zenodo-spacetime247CFE}.

### 2024-07-17 manuscript/sections/results.tex
license: add reuse compatibility
project: initial run pre-commit against all files
manuscript: working paper version

Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the region and the \enquote{demand pull} for advanced energy technologies.

>>>>

% SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
%
% SPDX-License-Identifier: CC-BY-4.0

Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
From the \gls{ci} buyers' perspective, we examine optimal procurement strategies for both annual and hourly matching strategies (i.e., a cost-optimal mix of locally procured energy generation, storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the background grid and the \enquote{demand pull} for advanced energy technologies.
